---
title: 'Class 7: R functions and packages'
author: "Ji H. Kang"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Functions revisited

we will source a file from online with our function from last day 
```{r}
source("http://tinyurl.com/rescale-R")
```



Try out the last day's rescale () function
```{r}
rescale(1:10)
```

Try the rescale2() function that catches string inputs
```{r}
rescale2(c(1:10),"string")
```

#Find missing NA values in teo vectors

Start with a simple example of the larger problem i am trying to solve
```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
```

```{r}
is.na(x)
```

```{r}
is.na(y)
```
 try putting these together an AND
```{r}
is.na(x) & is.na(y)
```
 
 Take the sum() to find out how many TRUE values we have and thus how many NAs we had in both x and y
```{r}
sum( is.na(x) )
```
 try putting these together 
```{r}
sum( is.na(x) & is.na(y) )
```
 

now i can make this into our first function
```{r}
both_na <- function(x,y){
  sum( is.na(x) & is.na(y) )
  
}
```

```{r}
both_na(x,c(NA,3,NA,2,NA))
```


test,test,test


```{r}
x <- c(NA, NA, NA)
y1 <- c( 1, NA, NA)
y2 <- c( 1, NA, NA, NA)
```

```{r}
both_na(x,y2)
```



```{r}
y3 <- c( 1, NA, NA, NA, NA, NA, NA, NA)
both_na(x,y3)
```

```{r}
3 !=2
```

```{r}
length(x)
```
```{r}
length(y2)
```



```{r}
which( c(F,F,T,F,F,F,T))


#which(is.na(c(1,2,NA,4)))
```



```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
both_na3(x,y)
```

##Intersect function
```{r}
df1
```

```{r}
df2
```
simplify further to single vectors

```{r}
x <- df1$IDs
y <- df2$IDs
```

now what do we do
```{r}
intersect(x,y)
```

```{r}
which (x %in% y)
```


```{r}
cbind(x[x %in% y],
      y[y %in% y])
```


use the Rstudio shortcut to turn our snippet into a working function
code- extract function
```{r}
gene_intersect <- function(x, y) {
  cbind(x[x %in% y],
        y[y %in% y])
}
```

```{r}
gene_intersect(x, y)
```
```{r}
gene_intersect2(df1,df2)
```

```{r}
gene_intersect3(df1,df2)
```


```{r}
merge(df1,df2, by="IDs")
```


In class hw 
Grade: to calculate the mean score + drop the single lowest score 

1) fine the minimum value of the vector
```{r}
student1 <- c(100,100,100,100,100,100,100,90)
student2 <- c(100,90,90,90,90,90,97,80)
```

```{r}
mean(student1)
```
```{r}
mean(student2)
```
 ##Grade function
 
```{r}
 x <- c(100,100,100,100,100,100,100,90)
```

worst score
```{r}
min(x)
```
```{r}
sum(x)-min(x)
```
```{r}
(sum(x)-min(x))/length((x)-1)

```
```{r}
sum(x)-min(x)/7

```




