---
title: 'Class 13'
author: "Ji H. Kang"
date: "5/14/2019"
output: github_document
---
Q5: What proportion of the Mexican Ancestry in Los Angeles sample population (MXL)
are homozygous for the asthma associated SNP (G|G)? 

```{r}
#Read CSV from ENSEMBLE
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378 (3).csv")
head(mxl)
```
How many of each genotype are there? 

```{r}
table(mxl$Genotype..forward.strand.)
```
Porportion or precent of total for each genotype

```{r}
(table(mxl$Genotype..forward.strand.)/ nrow(mxl)) * 100
```

Answer= 14% 


##Quality SCores in FASTQ files

The fourth line of a FASTQ sequence format file encodes the quality score that tells us how good the sequence at a given position is (i.e. how liekly it is to be correct based on the instrument)
```{r}
library(seqinr)
library(gtools)
#sc
phred <- asc( s2c("DDDDCDEDCDDDDBBDDDCC@") ) - 33
phred 
```


## Population Scale Analysis
Section 4

Read RNA-Seq data with genotype information results table

```{r}
expr <- read.table("rs8067378_ENSG00000172057.6.txt",row.names = 1)

head(expr)

```

Min/max/median values
```{r}
summary(expr)
```

Which samples are G/G?
```{r}
inds <- expr$geno == "G/G"
#true false
#return G/G
expr[inds,]
```

```{r}
inds <- expr$geno == "G/G"
#true false
#return G/G
expr[inds,"exp"]
```

```{r}
inds <- expr$geno == "G/G"

summary(expr[inds,"exp"])
```

```{r}
inds <- expr$geno == "A/G"

summary(expr[inds,"exp"])
```

```{r}
inds <- expr$geno == "A/A"

summary(expr[inds,"exp"])
```

BOXPLOT
```{r}
boxplot(exp ~ geno ,data=expr)
```
definitely a difference between the expression 
